\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}

\newtheorem{theorem}{Problem}

\begin{document}

\begin{theorem}
A triangle has sides measuring 1 unit and 3 units. The length of the third side is an integer value of units. What is the length of the third side, in units?
\end{theorem}

\begin{proof}
Step 0: We know that the sum of any two sides of a triangle must be greater than the third side.
Step 1: So, let's set up some inequalities. The first inequality will be $1+3>x$.
Step 2: The left side of the inequality simplifies to $4>x$.
Step 3: So, we know that $4>x$. Let's set up another inequality.
Step 4: The second inequality is $3+x>1$.
Step 5: That simplifies to $x>-2$.
Step 6: So we have the inequalities $4>x>-2$.
Step 7: Because x is a length, it must be positive.
Step 8: So, we know that $4>x>0$. Because x is an integer, it can only be 1, 2 or 3.
Step 9: So the length of the third side is either 1, 2 or 3 units.
Step 10: But if the length of the third side was 1, then the sum of the first two sides would be equal to the third side. That's not allowed.
Step 11: So, the length of the third side is 2 or 3 units.
Step 12: Because we can't have two answers, we need to check which of the two answers is correct.
Step 13: So, let's plug in 2 for the length of the third side and see if the inequality holds.
Step 14: The inequality we need to check is $1+3>2$.
Step 15: The left side of the inequality simplifies to $4>2$.
Step 16: So, we know that the inequality holds.
Step 17: But there's also an error here because 2+1 is not greater than 3.
Step 18: Right. So, we need to check the other answer. Let's plug in 3 for the length of the third side and see if the inequality holds.
Step 19: The inequality we need to check is 1+3>3.
Step 20: The left side simplifies to 4>3.
Step 21: So this inequality also holds.
Step 22: But we also have 3+1>3.
Step 23: So the answer is 4. I've made an error earlier; given the conditions, x could actually be 4
Step 24: So the length of the third side is 4 units.
\end{proof}

\end{document}
