\section{Discussion}
\label{sec:discussion}

\textbf{Limitations.}
This paper emphasizes helpfulness but largely neglects safety. Honesty and harmlessness are crucial for a chat assistant as well~\cite{bai2022training}. We anticipate similar methods can be used to evaluate these metrics by modifying the default prompt. Additionally, within helpfulness, there are multiple dimensions like accuracy, relevance, and creativity, but they are all combined into a single metric in this study. A more comprehensive evaluation can be developed by analyzing and separating these dimensions. 
We propose preliminary solutions to address the limitations and biases of LLM-as-a-judge in \Cref{sec:addressing_limitations}, but we anticipate more advanced methods can be developed.



\textbf{Data collection and release.}
\Cref{sec:data-collection} describes the detailed data collection and release processes, which include the instructions we give to users, the screenshots of the data collection interface, the information about participated users, and the content of the released data.

\textbf{Societal impacts.}
The societal impact of this study is multi-faceted. Our evaluation methods can help enhance chatbot quality and user experiences. However, addressing biases in these methods is crucial. Our dataset enables better studies of human preferences and model behavior. Advanced chat assistants may replace certain human tasks, resulting in job displacements and new opportunities.

\textbf{Future directions.}
1) Benchmarking chatbots at scale with a broader set of categories 2) Open-source LLM judge aligned with human preference 3) Enhancing open models' math/reasoning capability.

\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose LLM-as-a-judge for chatbot evaluation and systematically examine its efficacy using human preference data from 58 experts on MT-bench, as well as thousands of crowd-users on Chatbot Arena.
Our results reveal that strong LLMs can achieve an agreement rate of over 80\%, on par with the level of agreement among human experts, establishing a foundation for an LLM-based evaluation framework.

\section*{Acknowledgement}
This project is partly supported by gifts from Anyscale, Astronomer, Google, IBM, Intel, Lacework, Microsoft, MBZUAI, Samsung SDS, Uber, and VMware. Lianmin Zheng is supported by a Meta Ph.D. Fellowship.
We extend our thanks to Xinyang Geng, Hao Liu, Eric Wallace, Xuecheng Li, Tianyi Zhang, Qirong Ho, and Kevin Lin for their insightful discussions.


