\documentclass{article}
\usepackage{amsmath,amssymb}

\title{Asymptotic Behavior of Solutions to a Class of Nonlinear Differential Equations}
\author{Test Author}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We study the asymptotic behavior of solutions to the nonlinear ordinary differential equation
$u'' + f(u) = 0$, where $f$ satisfies standard growth and monotonicity conditions.
Under these assumptions, we establish that all bounded solutions converge to an equilibrium
as $t \to \infty$. Our proof relies on a Lyapunov functional argument combined with
the {\L}ojasiewicz--Simon inequality.
\end{abstract}

\section{Introduction}
The long-time behavior of solutions to nonlinear evolution equations has been studied extensively
in the past decades. A central question is whether bounded solutions converge to a single
equilibrium or exhibit more complicated dynamics such as oscillation or chaos.

For gradient-like systems, convergence to equilibrium can often be established using
Lyapunov methods. The key difficulty arises when the set of equilibria is not discrete,
in which case standard arguments guarantee convergence to the equilibrium set but not
to a single point. The {\L}ojasiewicz--Simon inequality, introduced by Simon~(1983)
building on earlier work of {\L}ojasiewicz~(1963), provides a powerful tool for resolving
this difficulty.

In this paper, we apply this approach to the equation
\begin{equation}\label{eq:ode}
u'' + f(u) = 0,
\end{equation}
where $f \colon \mathbb{R} \to \mathbb{R}$ is analytic and satisfies $f(0) = 0$.

\section{Assumptions and Main Result}

We impose the following conditions on the nonlinearity $f$.

\begin{enumerate}
\item[(A1)] $f \colon \mathbb{R} \to \mathbb{R}$ is real analytic.
\item[(A2)] There exists a primitive $F(u) = \int_0^u f(s)\,ds$ such that $F(u) \to +\infty$
as $|u| \to \infty$.
\end{enumerate}

Under these assumptions, we prove the following.

\begin{theorem}\label{thm:main}
Let $f$ satisfy conditions \emph{(A1)--(A2)}, and let $u$ be a bounded solution
of~\eqref{eq:ode} on $[0,\infty)$. Then there exists $u_\infty \in \mathbb{R}$ with
$f(u_\infty) = 0$ such that
\[
\lim_{t \to \infty} u(t) = u_\infty \quad \text{and} \quad \lim_{t \to \infty} u'(t) = 0.
\]
\end{theorem}

\section{Proof of the Main Result}

Define the energy functional
\[
E(t) = \tfrac{1}{2}\bigl(u'(t)\bigr)^2 + F\bigl(u(t)\bigr).
\]
A direct calculation shows that $E'(t) = 0$ along solutions of~\eqref{eq:ode},
so $E$ is constant. Since $u$ is bounded and $F(u) \to +\infty$ as $|u| \to \infty$,
the trajectory $\{(u(t), u'(t))\}$ is precompact. By the {\L}ojasiewicz--Simon inequality
applied to the analytic function $F$, convergence to a single equilibrium follows
by a standard argument (see, e.g., Haraux and Jendoubi, 2015).

\begin{proof}[Proof of Theorem~\ref{thm:main}]
The energy identity and precompactness imply that the $\omega$-limit set
$\omega(u)$ is a nonempty, connected, compact subset of the set of equilibria
$\{v : f(v) = 0\}$. By condition~(A1), this zero set is discrete (being the zero set
of a nonzero analytic function), so $\omega(u)$ is a single point $\{u_\infty\}$.
Convergence of $u'(t) \to 0$ follows from the energy identity and boundedness.
\end{proof}

\section{Conclusion}
We have established convergence to equilibrium for bounded solutions of a class of
nonlinear ordinary differential equations under analyticity and coercivity assumptions.
The argument extends naturally to damped equations of the form $u'' + \gamma u' + f(u) = 0$
with $\gamma > 0$, where the energy is strictly decreasing.

\end{document}
