\documentclass{article}
\usepackage{amsmath}

\title{Why Minimum Wage Laws Are Bad: A Super Quick Math Proof}
\author{Test Author}
\date{}

\begin{document}
\maketitle

\begin{abstract}
So basically everyone knows that minimum wage laws mess up the labor market.
In this paper I'm going to show you a really cool model that proves it.
My model is way better than what other people have done before.
Trust me, the math checks out.
\end{abstract}

\section{Introduction}
Minimum wage is a hot topic these days.
A bunch of economists have argued about it forever.
Some people think it's good, some think it's bad.
I personally think the evidence clearly shows it's bad, and I'll prove it here.

The rest of this paper is organized as follows.
Section 2 has the model.
Section 3 has some graphs I made.
Section 4 wraps things up.

\section{The Model}
OK so here's my model. Consider a labor market with supply $S(w) = aw$ and demand $D(w) = b - cw$
where $w$ is the wage. The equilibrium wage is obviously
\[
w^* = \frac{b}{a+c}.
\]
Now if we set a minimum wage $\bar{w} > w^*$ then clearly $S(\bar{w}) > D(\bar{w})$
which means there's unemployment. QED.

This is a really elegant result that demolishes the pro-minimum-wage argument.

\section{Empirical Evidence}
I looked at some data from the internet and it seems to confirm my model.
Figure~1 shows the relationship but I couldn't get the plotting software to work so you'll have to take my word for it.

Also Card and Krueger (1994) found the opposite but their methodology is super flawed in my opinion.

\section{Conclusion}
I've conclusively proven that minimum wage laws cause unemployment.
Policymakers should listen to economists like me instead of pushing ideological agendas.
This paper is definitely publishable in a top economics journal.

\end{document}
