\documentclass{article}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs} %

\usepackage{hyperref}

\usepackage{mathtools}

\DeclarePairedDelimiterX{\KLbase}[2]{(}{)}{%
  #1\;\delimsize\|\;#2%
}
\newcommand{\KL}{D\KLbase}


\newcommand{\theHalgorithm}{\arabic{algorithm}}


\newcommand{\fg}[1]{\textcolor{red}{fg: #1}}
\newcommand{\gab}[1]{\textcolor{green}{gab: #1}}
\newcommand{\broz}[1]{\textcolor{blue}{broz: #1}}
\newcommand{\badr}[1]{\textcolor{purple}{badr: #1}}

\usepackage[accepted]{icml2024}


\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}

\usepackage[capitalize,noabbrev]{cleveref}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\usepackage[textsize=tiny]{todonotes}


\newcommand{\supertitle}{Better \& Faster Large Language Models via Multi-token Prediction}
\icmltitlerunning{\supertitle{}}




















\usepackage[utf8]{inputenc} %
\usepackage[T1]{fontenc}    %
\usepackage{hyperref}       %
\usepackage{url}            %
\usepackage{booktabs}       %
\usepackage{amsfonts}       %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage{xcolor}         %
\usepackage{multirow}

\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{float}
\usepackage{enumitem}
\usepackage{bbm}    %
\usepackage{todonotes}

\long\def\intodo#1{\todo[inline]{#1}}

\newcommand{\point}[1]{{\noindent \color{purple} \scriptsize $\blacktriangleright$ #1}\par}
\newcommand{\todos}[1]{\noindent {{\colorbox{purple}{\color{white} \texttt{\textbf{TODO}}}} \color{purple} #1}}




\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\id}{id}
\DeclareMathOperator*{\Var}{Var}
\DeclareMathOperator*{\E}{\mathbb{E}}

\newcommand{\R}{\mathbb{R}}
\newcommand{\del}{\partial}
\newcommand{\iso}{\xrightarrow{\sim}}
\newcommand{\test}{\text{test}}
\newcommand{\val}{\text{val}}
\newcommand{\train}{\text{train}}

\begin{document}

\twocolumn[
\icmltitle{\supertitle{}}



\icmlsetsymbol{equal}{*}
\icmlsetsymbol{adv}{+}

\begin{icmlauthorlist}
\icmlauthor{Fabian Gloeckle}{equal,fair,ponts}
\icmlauthor{Badr Youbi Idrissi}{equal,fair,upsaclay}
\icmlauthor{Baptiste Rozière}{fair}
\icmlauthor{David Lopez-Paz}{adv,fair}
\icmlauthor{Gabriel Synnaeve}{adv,fair}
\end{icmlauthorlist}

\icmlaffiliation{fair}{FAIR at Meta}
\icmlaffiliation{ponts}{CERMICS Ecole des Ponts ParisTech}
\icmlaffiliation{upsaclay}{LISN Université Paris-Saclay}

\icmlcorrespondingauthor{Fabian Gloeckle}{fgloeckle@meta.com}
\icmlcorrespondingauthor{Badr Youbi Idrissi}{byoubi@meta.com}

\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

\printAffiliationsAndNotice{\icmlEqualContribution} %






\begin{abstract}
Large language models such as GPT and Llama are trained with a next-token prediction loss.
In this work, we suggest that training language models to predict \emph{multiple} future tokens at once results in higher sample efficiency.
More specifically, at each position in the training corpus, we ask the model to predict the following $n$ tokens using $n$ independent output heads, operating on top of a shared model trunk. 
Considering multi-token prediction as an auxiliary training task, we measure improved downstream capabilities with no overhead in training time for both code and natural language models.
The method is increasingly useful for larger model sizes, and keeps its appeal when training for multiple epochs. Gains are especially pronounced on \emph{generative} benchmarks like coding, where our models consistently outperform strong baselines by several percentage points. Our 13B parameter models solves 12~\% more problems on HumanEval and 17~\% more on MBPP than comparable next-token models. Experiments on small algorithmic tasks demonstrate that multi-token prediction is favorable for the development of induction heads and algorithmic reasoning capabilities.
As an additional benefit, models trained with 4-token prediction are up to $3\times$ faster at inference, even with large batch sizes.
\end{abstract}

\section{Introduction}
\input{intro}

\section{Method}
\input{method}

\section{Experiments on real data}
\input{results}

\section{Ablations on synthetic data}
\input{analysis}

\section{Why does it work? Some speculation}
\input{discussion}

\section{Related work}
\input{related}

\section{Conclusion}
\input{conclusion}

\section*{Impact statement}
\input{impact}

\section*{Environmental impact}
\input{carbon}

\section*{Acknowledgements}
\input{acks}

\clearpage



\bibliography{main}
\bibliographystyle{plainnat}

\clearpage
\newpage
\include{appendix}

\end{document}
