We have presented Gemini, a new family of models that advance multimodal model capabilities in text, code, image, audio, and video. Our most capable pre-trained model Gemini Ultra, alongside the post-trained Gemini Apps and Gemini API variants, make significant advances across the board. In the natural language domain, the performance gains from careful developments in data and model training at scale continue to deliver quality improvements, setting new state of the art in several benchmarks. In particular, Gemini Ultra surpasses human-expert performance on the exam benchmark MMLU, scoring 90.0\%, which has been a defacto measure of progress for LLMs ever since it was first released in 2020. In the multimodal domain, Gemini Ultra sets new state of the art on most of the image understanding, video understanding, and audio understanding benchmarks without task-specific modifications or tuning.In particular, Gemini Ultra’s multimodal reasoning capabilities are evident from its state-of-the-art performance on the recent MMMU benchmark~\cite{mmmu}, that comprises questions about images requiring college-level subject knowledge and deliberate reasoning.

Beyond the state-of-art results on benchmarks, what we are most excited about is the new use cases enabled by Gemini models. The new capabilities of Gemini models to parse complex images, such as charts or infographics, reason over interleaved sequences of images, audio, and text, and generate interleaved text and images as responses open a wide variety of new applications. As shown in figures throughout the report and appendix, Gemini models can enable new approaches in areas like education, everyday problem solving, multilingual communication, information summarization, extraction, and creativity. We expect that the users of these models will find all kinds of beneficial new uses that we have only scratched the surface of in our own investigations.

Despite their impressive capabilities, we should note that there are limitations to the use of LLMs. There is a continued need for ongoing research and development on ``hallucinations'' generated by LLMs to ensure that model outputs are more reliable and verifiable. LLMs also struggle with tasks requiring high-level reasoning abilities like causal understanding, logical deduction, and counterfactual reasoning even though they achieve impressive performance on exam benchmarks. This underscores the need for more challenging and robust evaluations to measure their true understanding as the current state-of-the-art LLMs saturate many benchmarks.

The Gemini family is a further step towards our mission to solve intelligence, advance science and benefit humanity, and we are enthusiastic to see how these models are used by our colleagues at Google and beyond. We build on many innovations in machine learning, data, infrastructure, and responsible development -- areas that we have been pursuing at Google for over a decade. The models we present in this report provide a strong foundation towards our broader future goal to develop a large-scale, modularized system that will have broad generalization capabilities across many modalities.
